Mechanization of Separation in Generic Extensions

### 2019-04-01 ITP/Separation_In_MG.tex
IEEE
link a sources
typo cerca de nombre Manu

\author{Emmanuel Gunther}{FAMAF, Universidad Nacional de Córdoba, [optional: Address], Argentina}{gunther@famaf.unc.edu.ar}{}{Partially supported by a CONICET scholarship}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

@@

\supplement{The whole Isabelle/ZF development is available at \url{https://arxiv.org/abs/1901.03313}}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)
\usepackage{isabelle,isabellesym}
\usepackage{csquotes}
\input{header-draft}

@@

\newpage
\onecolumn
\appendix[A short overview of our development]
\input{appendix}

>>>>

\author{Emmanuel Gunther}{FAMAF, Universidad Nacional de Córdoba, Argentina}{gunther@famaf.unc.edu.ar}{}{Partially supported by a CONICET scholarship}%TODO mandatory, please use full name; only 1 author per \author macro; first two parameters are mandatory, other parameters can be empty. Please provide at least the name of the affiliation and the country. The full address is optional

@@

\supplement{The whole Isabelle/ZF development is available at \url{https://cs.famaf.unc.edu.ar/\~{}mpagano/forcing/}}%optional, e.g. related research data, source code, ... hosted on a repository like zenodo, figshare, GitHub, ...

@@

%Editor-only macros:: begin (do not touch as author)%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
\EventEditors{John Q. Open and Joan R. Access}
\EventNoEds{2}
\EventLongTitle{42nd Conference on Very Important Topics (CVIT 2016)}
\EventShortTitle{CVIT 2016}
\EventAcronym{CVIT}
\EventYear{2016}
\EventDate{December 24--27, 2016}
\EventLocation{Little Whinging, United Kingdom}
\EventLogo{}
\SeriesVolume{42}
\ArticleNo{23}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Some very useful LaTeX packages include:
% (uncomment the ones you want to load)
\usepackage{isabelle,isabellesym}
\usepackage{csquotes}
\input{header-draft}
\IEEEtrue

@@

\newpage
\onecolumn
\appendix
\section{A short overview of our development}
\input{appendix}
